\huge I don't know, are you sure we want to do this? Sea level adaptation decisions under uncertainty

### 2017-01-31 techreport/paper.tex
minor correction

\aboutauthors{Thordis L. Thorarinsdottir is Chief Research Scientist and Peter Guttorp is Professor II at the Norwegian Computing Center in Oslo, Norway. Martin Drews is a Senior Scientist and Per Skougaard Kaspersen is Postdoc at DTU Management Engineering, Technical University of Denmark in Copenhagen, Denmark. Karianne de Bruin is a Senior Researcher at the Center for International Climate and Environmental Research in Oslo, Norway and Researcher at Wageningen Environmental Research in Wageningen, The Netherlands}

>>>>

\aboutauthors{Thordis L. Thorarinsdottir is Chief Research Scientist and Peter Guttorp is Professor II at the Norwegian Computing Center in Oslo, Norway. Martin Drews is a Senior Scientist and Per Skougaard Kaspersen is Postdoc at DTU Management Engineering, Technical University of Denmark in Copenhagen, Denmark. Karianne de Bruin is Senior Researcher at the Center for International Climate and Environmental Research in Oslo, Norway and Researcher at Wageningen Environmental Research in Wageningen, The Netherlands}
